---
title: "Unit Conversions"
# author: "Your Name" # Optionally take some credit for submitting a question!
difficulty: 0.3
tags:
  - vectors
details: >
  Convert a timespan in years to more human-readable timespans
---


# Question

You're given a numeric vector of ages in years for people ranging from just a
few seconds old to nearly 100 years old. For printing, you would prefer to use
the largest unit for which the age rounds down to a positive integer (e.g. **"33
mins old"** instead of **"6.46e-5 years old"**). Additionally, you want to
indicate a plural unit when the next lowest positive integer is greater than 1.

For unit conversions, a numeric vector, `conversions`, has been provided to
convert from years according to the following conversions:

```{}
conversions <- c(
  year  = 1,                #  1 year  =  1 year
  month = 365.25/30.5,      #  1 year  =  365.25 days
  week  = 365.25/7,         #  1 week  =  7 days
  day   = 365.25,           #  1 month =  30.5 days
  hour  = 365.25*24,        #  1 day   =  24 hours
  min   = 365.25*24*60,     #  1 hour  =  60 mins
  sec   = 365.25*24*60*60)  #  1 min   =  60 secs
```

For example, given the following ages in years

```{}
ages <- c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1, 1, 10)
```

Your resulting character vector would be 

```{}
c("31 secs old", "5 mins old", "52 mins old", "8 hours old", "3 days old", 
    "1 month old", "1 year old", "10 years old")
```




```{r grader}
conversions <- c(
  year = 1, 
  month = 365.25/30.5,
  week = 365.25/7,
  day = 365.25,
  hour = 365.25*24,
  min = 365.25*24*60,
  sec = 365.25*24*60*60)

test_inputs <- list(
  list(conversions = conversions,
    ages = c(0.000001, 0.00001, 0.0001, 0.001, 0.01, 0.1, 1, 10)),
  # test example input
  list(conversions = conversions, 
    ages = 1*10 ^ (-6:1)),
  # test random input
  list(conversions = conversions, 
    ages = 1*10 ^ runif(5, min = -6, max = 2)),
  # test case len(ages) == 1
  list(conversions = conversions, 
    ages = 1*10 ^ runif(1, min = -6, max = 2)),
  # test long input
  list(conversions = conversions, 
    ages = 1*10 ^ runif(5000, min = -6, max = 2)))

list(
  test_inputs = test_inputs,
  test_timeouts = 0.1,
  solution = quote({
    m <- floor(ifelse((m <- ages %*% t(conversions)) >= 1, m, NA))
    i <- apply(m, 1, Position, f = Negate(is.na))
    v <- setNames(Map("[", split(m, row(m)), i), colnames(m)[i])
    paste0(v, " ", names(v), ifelse(v>1, "s", ""), " old")
  }),
  quoted = TRUE)
```

```{r starter, eval = FALSE}
# already in environment:
#   ages (numeric vector; 0.000001 <= value <= 100; 1 <= length <= 10,000)
#   conversions (named numeric vector of unit conversions [n/year])

print(ages)
print(round(conversions))
```

